Gafo-cc data processing

### 2023-07-30 analysis/gafo-cc-data-processing.Rmd
chimfunshi model comparison prep

# Merge
```{r}

data <- bind_rows(
  data_zambia,
  data_namibia%>%rename(younger_children = youngerchildren),
  data_leipzig,
  data_nigeria,
  data_plymouth,
  data_stanford,
  data_mex,
  data_china, 
  data_arg,
  data_ind,
  #data_nz
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test",
         voiceover == F
         )%>%
  mutate(age_group = substr(ageinyears, 1,1), 
         trialnr = as.numeric(factor(trialnr)))%>%
  select(subjid, community, age_group, ageinyears, sex, screen, touchscreen, household, children, younger_children, trialnr, targetposition,targetcenterx, targetcentralityx, clickdistfromtargetcenterx)%>%
  filter(ageinyears > 1)

@@

data%>%
  #group_by(community)%>%
  summarise(n = n_distinct(subjid))
```

```{r}
data%>%
  filter(touchscreen == 2)%>%
  distinct(subjid)

@@

```{r}

data <- read_csv("../data/gafo-cc-clean-data.csv")

haillom_data <- data%>%
  filter(community == "hai||om",
         voiceover == F)%>%
  mutate(agecentered = ageinyears - min(ageinyears))%>%
  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site,`location` ))

>>>>

# Merge
```{r}
merge_raw_data <- bind_rows(
  data_zambia,
  data_namibia%>%rename(younger_children = youngerchildren),
  data_leipzig,
  data_nigeria,
  data_plymouth,
  data_stanford,
  data_mex,
  data_china, 
  data_arg,
  data_ind,
  #data_nz
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test",
         voiceover == F
         )%>%
  mutate(age_group = substr(ageinyears, 1,1), 
         trialnr = as.numeric(factor(trialnr)))

write_csv(merge_raw_data,"../data/gafo-cc-raw-data.csv")

data <- merge_raw_data%>%
  select(subjid, community, age_group, ageinyears, sex, screen, touchscreen, household, children, younger_children, trialnr, targetposition,targetcenterx, targetcentralityx, clickdistfromtargetcenterx)%>%
  filter(ageinyears > 1)

@@

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")

data%>%
  #group_by(community)%>%
  summarise(n = n_distinct(subjid))

data%>%
  filter(touchscreen == 2)%>%
  distinct(subjid)

@@

```{r}
merge_raw_data <- read_csv("../data/gafo-cc-raw-data.csv")
```

```{r}
chimfunshi_data <- merge_raw_data%>%
  filter(community == "chimfunshi",
         voiceover == F)%>%
  mutate(agecentered = ageinyears - min(ageinyears))%>%
  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site,`location` ))

write(toJSON(chimfunshi_data), file = "../model/model_data/chimfunshi-model-data.json")
```

```{r}
haillom_data <- merge_raw_data%>%
  filter(community == "hai||om",
         voiceover == F)%>%
  mutate(agecentered = ageinyears - min(ageinyears))%>%
  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site,`location` ))
